The evolution of gene expression in the term placenta of viviparous mammals

### 2015-11-21 manuscript/manuscript.Rnw
get rid of duplication of go analysis in the ouch bit

To determine enrichment of functional categories in lists of genes
that display a significant shift in expression on a specific branch,
we performed functional annotation cluster analyses on each branch
using DAVID
\cite{Huang.ea2009:Systematicandintegrativeanalysis,Sherman.ea2007:DAVIDKnowledgebasegene-centereddatabase}.
DAVID ranks functional annotation clusters according to enrichment
score (ES); functional annotation clusters are considered
significantly enriched if $\mathrm{ES}\ge1.3$, as this corresponds to
$p\le0.05$ \cite{Huang.ea2009:Systematicandintegrativeanalysis}. As
above, due to the paucity of annotated gene ontology terms for some
species, gene lists were compared using gene ontology terms derived
from the human genome.

>>>>

We also calculated the enrichment of functional categories in the
lists of genes which displayed a significant shift in expression on
each branch using the same methodology as in the per-species gene
lists \DLA{reference the tables once this analysis is complete}.
